Conformance Checking Using Embeddings and its Applicability in the Internet of Things

### 2021-12-22 paper.tex
Updated slides

All experiments utilized (the same) randomly generated process trees, that were constructed using the algorithms in the \emph{pm4py} library.
Three size configurations described by minimum number, the model, and the maximum number of visible activities were chosen: 5-10-15, 10-20-30, and 15-30-45.
Furthermore, four operator configurations were chosen described by the probability for randomly choosing each available operator.
These were in no particular order: Sequence: $0.75$, Parallel $0.25$, secondly Sequence: $0.75$, Choice $0.25$, thirdly 1. Sequence: $0.5$, Parallel $0.25$, Choice $0.25$ and lastly $0.25$ for all (Sequence, Parallel, Choice and Loop) operators.
Both of these configurations were combined to generate a grid of $12$ process trees, with the hope that these cover a sufficient range of different behavior.
An example of such a random process tree is shown in \cref{fig:process-tree}
\footnote{Note that this tree is not the one used by the authors since they did not share their trees or logs, but one generated with the same parameters.}.

@@

\subsection{Scalability Experiment}
\begin{figure}
	\includegraphics[width=1\textwidth]{figures/scaling}
	\caption{Runtimes for all three methods for varying sizes of logs and dictionaries. Data can be found in \cite{MuCa10} Table 2.}
	\label{fig:scalability}
\end{figure}
The first performed experiment aimed to assess the performance  of the three proposed methods.
The experiments were run on an Intel Core i7-9850h, a mid-range consumer CPU.
Experiments were run for all three methods for different sized logs and different sized dictionaries, for embedding-based conformance checking algorithms dictionary size is determined by the number of different activities in the log.
All experiments were performed in Python, however, the Word Mover's distance was calculated using pyemd, a Python wrapper to calculate the WMD/EMD with NumPy efficiency.
As such, when comparing ICT and WMD times, the efficiency difference between Python and C should be taken into account.

>>>>

All experiments utilized (the same) randomly generated process trees, that were constructed using the algorithms in the \emph{pm4py} library.
Three size configurations described by minimum number, the model, and the maximum number of visible activities were chosen: 5-10-15, 10-20-30, and 15-30-45.
Furthermore, four operator configurations were chosen described by the probability for randomly choosing each available operator.
These were in no particular order: Sequence: $0.75$, Parallel $0.25$, secondly Sequence: $0.75$, Choice $0.25$, thirdly Sequence: $0.5$, Parallel $0.25$, Choice $0.25$ and lastly $0.25$ for all (Sequence, Parallel, Choice and Loop) operators.
Both of these configurations were combined to generate a grid of $12$ process trees, with the hope that these cover a sufficient range of different behavior.
An example of such a random process tree is shown in \cref{fig:process-tree}
\footnote{Note that this tree is not the one used by the authors since they did not share their trees or logs, but one generated with the same parameters.}.

@@

\subsection{Scalability Experiment}
\begin{figure}
	\includegraphics[width=1\textwidth]{figures/scaling}
	\caption{Runtimes for all three methods for varying sizes of logs and dictionaries. Data can be found in \cite{PBWe20} Table 2.}
	\label{fig:scalability}
\end{figure}
The first performed experiment aimed to assess the performance  of the three proposed methods.
The experiments were run on an Intel Core i7-9850h, a mid-range consumer CPU.
Experiments were run for all three methods for different sized logs and different sized dictionaries, for embedding-based conformance checking algorithms dictionary size is determined by the number of different activities in the log.
All experiments were performed in Python, however, the Word Mover's distance was calculated using pyemd, a Python wrapper to calculate the WMD/EMD with NumPy efficiency.
As such, when comparing ICT and WMD times, the efficiency difference between Python and C should be taken into account.
